Which Factors are Associated with Wikipedia Relevancy?

### 2024-11-27 paper/paper.qmd
updates paper code and pdf

# Filter to the top 5 subregions by count for each time_period
top5_subregions <- cleaned_data_filtered |>
  group_by(time_period) 
  slice_max(order_by = n, n = 5) |>
  ungroup()

@@

```{r}
#| eval: true
#| echo: false
#| message: false
#| warning: false
#| label: fig-ppcheckandposteriorvsprior
#| layout-ncol: 2
#| fig-cap: "Examining how the model fits, and is affected by, the data"
#| fig-subcap: ["Posterior prediction check", "Comparing the posterior with the prior"]

pp_check(first_model) +
  theme_classic() +
  theme(legend.position = "bottom")

posterior_vs_prior(first_model) +
  theme_minimal() +
  scale_color_brewer(palette = "Set1") +
  theme(legend.position = "bottom") +
  coord_flip()
```

## Diagnostics

@fig-stanareyouokay-1 is a trace plot. It shows... This suggests...

@fig-stanareyouokay-2 is a Rhat plot. It shows... This suggests...

```{r}
#| echo: false
#| eval: true
#| message: false
#| warning: false
#| label: fig-stanareyouokay
#| fig-cap: "Checking the convergence of the MCMC algorithm"
#| fig-subcap: ["Trace plot", "Rhat plot"]
#| layout-ncol: 2

plot(first_model, "trace")

plot(first_model, "rhat")
```

>>>>

# Filter to the top 5 subregions by count for each time_period
top5_subregions <- cleaned_data_filtered |>
  group_by(time_period) |>
  slice_max(order_by = n, n = 5) |>
  ungroup()

@@

<!-- ```{r} -->
<!-- #| eval: true -->
<!-- #| echo: false -->
<!-- #| message: false -->
<!-- #| warning: false -->
<!-- #| label: fig-ppcheckandposteriorvsprior -->
<!-- #| layout-ncol: 2 -->
<!-- #| fig-cap: "Examining how the model fits, and is affected by, the data" -->
<!-- #| fig-subcap: ["Posterior prediction check", "Comparing the posterior with the prior"] -->

<!-- pp_check(first_model) + -->
<!--   theme_classic() + -->
<!--   theme(legend.position = "bottom") -->

<!-- posterior_vs_prior(first_model) + -->
<!--   theme_minimal() + -->
<!--   scale_color_brewer(palette = "Set1") + -->
<!--   theme(legend.position = "bottom") + -->
<!--   coord_flip() -->
<!-- ``` -->

<!-- ## Diagnostics -->

<!-- @fig-stanareyouokay-1 is a trace plot. It shows... This suggests... -->

<!-- @fig-stanareyouokay-2 is a Rhat plot. It shows... This suggests... -->

<!-- # ```{r} -->
<!-- # #| echo: false -->
<!-- # #| eval: true -->
<!-- # #| message: false -->
<!-- # #| warning: false -->
<!-- # #| label: fig-stanareyouokay -->
<!-- # #| fig-cap: "Checking the convergence of the MCMC algorithm" -->
<!-- # #| fig-subcap: ["Trace plot", "Rhat plot"] -->
<!-- # #| layout-ncol: 2 -->
<!-- # -->
<!-- # plot(first_model, "trace") -->
<!-- # -->
<!-- # plot(first_model, "rhat") -->
<!-- # ``` -->
<!-- # -->
